Fast and adaptive cointegration based model for forecasting high frequency financial time series

### 2017-02-01 articles-conferences/iscef2016/body.tex
first version of editor letter

Cointegration relationships can be found in low and high frequency data of two or
more assets. While cointegration in low frequency data is motivated by a
long-run equilibrium relationship between economic forces, cointegration in high
frequency data has its foundation in statistical arbitrage which is very helpful
to detect mean-reverting trades. Information about cointegrated assets in high
frequency data could be used as an input for high frequency trading strategies,
using it as a signal to capture small profits in short term trades, see
\cite{miao2014}. \cite{zhou2001} addressed the benefits of using higher
frequency data to analize cointegration. \cite{rittler2012} also found that
cointegration may differ with different data frequencies and could appear
whith increased data frequency.

>>>>

Cointegration relationships can be found in low and high frequency data of two or
more assets. While cointegration in low frequency data is motivated by a
long-run equilibrium relationship between economic forces, cointegration in high
frequency data has its foundation in statistical arbitrage theory which is very helpful
to detect mean-reverting trades. Information about cointegrated assets in high
frequency data could be used as an input for high frequency trading strategies,
using it as a signal to capture small profits in short term trades, see
\cite{miao2014}. \cite{zhou2001} addressed the benefits of using higher
frequency data to analize cointegration. \cite{rittler2012} also found that
cointegration may differ with different data frequencies and could appear
whith increased data frequency.
